### 2025-09-04 YEAR2/PHY293_LectureNotes/main.tex
pre year2
4 sept

\documentclass[11pt]{report}
\input{preamble}
\begin{document}
\thispagestyle{empty}
{\LARGE \bf MAT 292 Lecture Notes}\\
{\large Hei Shing Cheung}\\
Ordinary Differential Equations, Fall 2025 \hfill MAT292\\
\\
The up-to-date version of this document can be found at \url{https://github.com/HaysonC/skulenotes}\\
\end{document}

>>>>

\documentclass[11pt]{report}
\input{preamble}
\begin{document}
\thispagestyle{empty}
{\LARGE \bf PHY 293 Lecture Notes}\\
{\large Hei Shing Cheung}\\
Waves and Modern Physics, Fall 2025 \hfill PHY293\\
\\
The up-to-date version of this document can be found at \url{https://github.com/HaysonC/skulenotes}\\

\chapter{Waves}
\section{Harmonic Oscillators}

\subsection{Governing Equations of Harmonic Oscillators}

\paragraph{Types of Harmonic Oscillators} There are three types of harmonic oscillators: simple, damped, and driven harmonic oscillators. Consider a simple one dimensional harmonic oscillator, they are defined by the following differential equations:

\begin{definition}[Simple Harmonic Oscillator]
    A simple harmonic oscillator is described by Hooke's law:

    \begin{equation}
        m \frac{d^2 x}{dt^2} + kx = 0
    \end{equation}
    where \( k \) is the spring constant, \( m \) is the mass, and \( x \) is the displacement from equilibrium.
\end{definition}

\begin{definition}[Damped Harmonic Oscillator]
    A damped harmonic oscillator is described by the following differential equation, by adding a damping term proportional to $\dot{x}$ to the simple harmonic oscillator equation:
    \begin{equation}
        m \frac{d^2 x}{dt^2} + \gamma \frac{dx}{dt} + kx = 0   
    \end{equation}
    where \( \gamma \) is the damping coefficient.
\end{definition}

\begin{definition}[Driven Harmonic Oscillator]
    A driven harmonic oscillator is described by the following differential equation, which includes an external driving force $F(t)$:
    \begin{equation}
        m \frac{d^2 x}{dt^2} + \gamma \frac{dx}{dt} + kx = F(t)   
    \end{equation}
\end{definition}
\subsection{The Wave Equation}

\begin{definition}[The Wave Equation]
    The wave equation is a second-order linear partial differential equation that describes the propagation of waves, such as sound waves, light waves, and water waves, through a medium. In one dimension, it is given by the following PDE:
    \begin{equation}
        \frac{\partial^2 u}{\partial t^2} - c^2 \frac{\partial^2 u}{\partial x^2} = 0
    \end{equation}
    where \( u(x,t) \) is the wave function, \( c \) is the speed of the wave in the medium, \( x \) is the spatial coordinate, and \( t \) is time.
\end{definition}

\chapter{Modern Physics}
\end{document}
